---
title: "Macroeconometrics - Homework 4"
author: "Gabriel Konecny"
date: "2023-06-03"
output: pdf_document
---

#Exercise 1

For this exercise we tried to change $\lambda_1$ holding $\lambda_2$ constant, then varying $\lambda_2$ holding $\lambda_1$, and then varying both $\lambda_1$ and $\lambda_2$. For each of those, we compare 6 different values of lambda. The corresponding coefficients are depicted in the first 3 figures in Appendix.

Changes in the estimated AR coefficients:

For small values of $\lambda_1$ given $\lambda_2$, we see that all AR coefficients except constant are pushed towards their expectation given by $\underline{A}$ strongly. For each variable, its first lag is close to one and all other coefficients are close to 0. For high values of $\lambda_1$, the distinction between the coefficients of own first lags and others gets less pronounced. This was expected since in Minnesota prior $\lambda_1$ induces global shrinkage for all parameters except the constant term.
Low value of $\lambda_2$ pushes the cross-variable coefficients to 0, while the own-variable coefficients have more freedom given by a medium value of $\lambda_1$. For high values of $\lambda_2$, the cross-variable coefficients fluctuate more freely around 0.
Varying $\lambda_1$ and $\lambda_2$ combines these two effects.

Changes in the estimated IRFs (we use Cholesky for illustration):

Low $\lambda_1$ pushes all median IRFs to a constant response since all coefficients except for constant are pushed strongly to 0. Low $\lambda_2$ pushes the cross-variable responses to a constant. High $\lambda_1$ and $\lambda_2$ let the data speak. Notice that in Cholesky, the right-upper triangle of IRFs starts at 0 by definition, thus they are pushed towards 0.

Changes in forecast:

Low $\lambda_1$ makes the forecasts look more like a random walk. Low $\lambda_2$ not necessarily, since the dependence on own lags and constant seem to cause substantial variation in the forecasts.


\newpage

# Exercise 2  

*Read Kilian (2009), who discusses how to disentangle different oil shocks; focus on section II. Load the provided data by Kilian (2009), which contains a measure of change in oil production, a measure of real economic activity, and the real price of oil.*

## Subquestion 2.1
*Using the code for the Bayesian VAR, estimate the VAR described in section II.A.*
Using the provided code from the lecture, we estimate the Bayesian VAR based on Kilian (2009). We increased the $\lambda_1$ to 0.6 to account for higher frequency of the data. The lag shrinkage in the formula of $V$ in Minnesota prior is given by $1/k$ where $k$ is the lag. This shrinkage is specific to quarterly or yearly data so for monthly data less aggressive lag shrinkage like 6/k is appropriate. To implement this we simply set $\lambda_1$ to 0.6 instead of 0.1. 
 
```{r load packages, echo=FALSE, include=FALSE}
rm(list=ls())
# -------------------------------------------------- #
#                                                    #
# Macroeconometrics Science Track Summer Term 2023   #
# Bayesian Vector Autoregressions                    #
# May 2023                                           #
#                                                    #
# Initial Code Credits to Maximiliam Böck            #
# ---------------------------------------------------#

###----------------------------------- Load packages -------------------------------------------------

if(suppressWarnings(!require(bvarsv))){
  install.packages("bvarsv")
}

if(suppressWarnings(!require(MCMCpack))){
  install.packages("MCMCpack")
}

if(suppressWarnings(!require(magic))){
  install.packages("magic")
}

if(suppressWarnings(!require(tidyverse))){
  install.packages("tidyvers")
}

require(bvarsv)
```

```{r data, echo=FALSE, include=FALSE}
############# NEW DATA  #############
data.kilian.raw <- read.table("data_kilian_park_2009.txt", header = FALSE, sep = "", col.names = c("prod","REA","RP","RDG"))
data.kilian <- ts(data.kilian.raw[,1:3], start = c(1973,1), frequency = 12)
############ NEW DATA #############

Traw <- nrow(data.kilian)
Yraw <- data.kilian

```

```{r transform and OLS, echo=FALSE, include=FALSE}
#------------------------------------------------------------------------------------
# useful function for lagging data matrices
mlag <- function(X,lag){
  p <- lag
  X <- as.matrix(X)
  Traw <- nrow(X)
  N <- ncol(X)
  Xlag <- matrix(0,Traw,p*N)
  for (ii in 1:p){
    Xlag[(p+1):Traw,(N*(ii-1)+1):(N*ii)]=X[(p+1-ii):(Traw-ii),(1:N)]
  }
  return(Xlag)
}
#######################################################################################
### Independent normal-Wishart prior for the VAR
######################################################################################
# needed libraries
library(MCMCpack) # has the inverse wishart riwish()
library(magic)

# specifications
plag <- 24     # number of lags
cons <- TRUE  # include constant?

# Create data matrices
Yraw <- as.matrix(Yraw)
Xraw <- mlag(Yraw, plag) # X's are the lagged values of Y

if(cons) Xraw <- cbind(Xraw, 1) # Note that constant is located after lags of variables

# look at size of data
dim(Yraw)
dim(Xraw)

# first plag rows are zero | conditioning on the first p observations
Y <- Yraw[(plag + 1):nrow(Yraw), ]
X <- Xraw[(plag + 1):nrow(Xraw), ]
y <- as.vector(Y)

dim(Y)
dim(X)
# View(X)

# get useful dimensions
M    <- ncol(Y)           # number of endogenous variables in the VAR
bigT <- nrow(Y)           # sample size, do not use T only as name!
K    <- M * plag          # number of autoregressive coefficients
k    <- ncol(X)           # number of parameters per equation
v    <- M * (M - 1) / 2
#------------------------------------------------------------------------------------
# Initial Values, OLS preliminaries, can also just take a draw from the prior distribution
#------------------------------------------------------------------------------------
A_OLS <- solve(crossprod(X)) %*% crossprod(X, Y)
# A_OLS <- chol2inv(chol(crossprod(X)))%*%crossprod(X,Y) 
# Cholesky to inverse saves computation time
E_OLS <- Y - X %*% A_OLS
S_OLS <- crossprod(E_OLS) / (bigT - K)

# let's have a look at OLS estimates
yfit <- X %*% A_OLS
# amazing in-sample fit, but bad out-of-sample fit
library(zoo)
time <- as.yearqtr(time(data.kilian))



# explained variation
diag(crossprod(yfit)) / diag(crossprod(Y))
```

```{r main 1, echo=FALSE, include=FALSE}
#------------------------------------------------------------------------------------
# PRIORS
#------------------------------------------------------------------------------------
A_prior <- matrix(0, k, M) 
diag(A_prior) <- 1 # prior mean: 1 for first own lags, 0 otherwise. Note that prior mean for
                   # deterministics is in last row due to ordering of constant in Xraw
A_prior
a_prior <- as.vector(A_prior) # vectorize prior mean matrix

# get AR variances to scale cross-variable lags of Minnesota prior
sigs <- numeric(length = M)
for(mm in 1:M){
  yuse <- Y[, mm, drop=FALSE]
  xuse <- cbind(X[,seq(mm, M * plag, by=M), drop=FALSE], 1)
  b    <- solve(crossprod(xuse)) %*% crossprod(xuse,yuse)
  sigs[mm] <- crossprod(yuse-xuse %*% b) / (bigT - plag - 1)
}

# Minnesota prior
# own lags:       (lambda1/k)^2   # k == lag
# cross lags:     (sig_i^2/sig_j^2)(lambda1 * lambda2/k)^2
# deterministics: lambda3*sig_i^2
lambda1 <- 0.6; lambda2 <- 0.5; lambda3 <- 100
V_prior <- array(0, c(k, k, M))
for(mm in 1:M){ # over all equations
  for(pp in 1:plag){ # over all lags
    for(kk in 1:M){ # over all coefficients
      if(mm == kk){ # own lag
        V_prior[(pp - 1) * M + kk, (pp - 1) * M + kk, mm] <- (lambda1 / pp)^2
      }else{ # cross-lags
        V_prior[(pp - 1) * M + kk, (pp - 1) * M + kk, mm] <- (sigs[mm] / sigs[kk]) * (lambda1 * lambda2 / pp)^2
      }
    }
  }
  V_prior[k, k, mm] <- lambda3 * sigs[mm] # for deterministics (i.e. constant)
}
V_prior    <- lapply(seq(dim(V_prior)[3]), function(x) V_prior[ , , x]) # array to list
V_prior    <- Reduce(magic::adiag, V_prior) # bring in form
V_prior[1:(M*plag+1), 1:(M*plag+1)]
V_priorinv <- diag(1 / diag(V_prior))

# hyperparameters for inverse Wishart
s0 <- M + 2
S0 <- (s0 - M - 1) * diag(sigs)

# initialize draws with OLS estimators
A_draw <- A_OLS
S_draw <- S_OLS

# outside loop calculations
s_post    <- bigT + s0
XX <- crossprod(X)


#------------------------------------------------------------------------------------
# MCMC setup
#------------------------------------------------------------------------------------
nsave <- 100               # number of saved draws
nburn <- 50               # number of burned draws
ntot  <- nsave + nburn      # number of total draws
nhor  <- 16                # horizon for IRFs
fhorz <- 8                  # forecasting horizon

# Container for MCMC draws, stored after burn-in
A_store <- array(NA, c(nsave, k, M))
S_store <- array(NA, c(nsave, M, M))
E_store <- array(NA, c(nsave, bigT, M))

# container for sign restriction attempts
cou_store <- numeric(length = nsave)

# Predictions -- dimensions: number of draws x number of variables x forecasting horizon
yf_store <- array(NA, c(nsave, M, fhorz))

# IRFs -- dimensions: Number of draws x Number of responses x Number of structural shocks x horizon
IRFchol_store <- array(NA,c(nsave, M, M, nhor))
IRFsign_store <- array(NA,c(nsave, M, M, nhor))

set.seed(1)
for(irep in 1:ntot){
  #-----------------------------------------------------------------------------
  # Step 1: Draw S_draw | Y, A_draw from IW
  # s_overbar = T + s_underbar (s0)
  # S_overbar = (Y-XA)'(Y-XA) + S_underbar (S0)
  # SIGMA | Y ~ iW(s_overbar,S_overbar)
  E_draw <- Y - X %*% A_draw
  S_post    <- crossprod(Y - X %*% A_draw)
  S_drawinv <- matrix(rWishart(1,s_post,solve(S_post)),M,M) 
  # note that we can draw from the Wishart and inverting leads to the inverse-Wishart
  S_draw    <- solve(S_drawinv) 
  # or using the MCMCpack to draw from inverse-Wishart directly
  S_draw    <- MCMCpack::riwish(s_post, S_post)

  #-----------------------------------------------------------------------------
  # Step 2: Draw A_draw | Y, S_draw from multivariate normal
  # V_overbar = (SIGMAinv otimes X'X + Vinv_underbar)^{-1}
  # a_overbar = V_overbar (Vinv_underbar a_underbar + (SIGMAinv otimes X')y)
  V_post    <- solve(kronecker(S_drawinv, XX) + V_priorinv)
  # Here, using chol2inv(chol(kronecker(S_drawinv, XX) + V_priorinv)) saves time
  A_post    <- V_post %*% (kronecker(S_drawinv, t(X))%*%y + V_priorinv%*%a_prior)
  
  eig_check <- TRUE
  while(eig_check) {
    # Here, using the lower Cholesky factor multiplied by k * M Normal draws creates
    # draws from the multivariate Normal and saves time, compared to drawing from 
    # multivariate Normal directly
    A_draw     <- matrix(A_post + t(chol(V_post)) %*% rnorm(k * M), k, M)
    # stability check using companion form
    Cm <- matrix(0, K, K)
    Cm[1:M,] <- t(A_draw[1:K, ]) # companion matrix excludes deterministic terms
    diag(Cm[(M + 1):K, 1:(M * (plag - 1))]) <- 1
    
    eig_check <- max(abs(Re(eigen(Cm)$values))) > 1
  }
  
  #-----------------------------------------------------------------------------
  # Step 3: Storage/Predictions/IRFs
  if(irep > nburn){
    # Step 3a: Save parameter draws
    A_store[irep - nburn, , ] <- A_draw
    S_store[irep - nburn, , ] <- S_draw
    E_store[irep - nburn, , ] <- E_draw

    #---------------------------------------------------------------------------
    # Step 3b: Build companion matrix for forecasts and IRFs again (illustration)
    Cm <- matrix(0, K, K)
    Cm[1:M,] <- t(A_draw[1:K, ]) # companion matrix excludes deterministic terms
    diag(Cm[(M + 1):K, 1:(M * (plag - 1))]) <- 1
    Jm <- matrix(0, K, M)
    diag(Jm) <- 1

    #---------------------------------------------------------------------------
    # Step 3c: Do predictions and calculate fhorz-step ahead prediction density
    Mean00  <- c(Y[bigT, ], X[bigT, 1:(M * (plag - 1))]) 
    # take latest values for Y plus p-1 lags from X for forecasts
    Sigma00 <- matrix(0, K, K)
    for(ihorz in 1:fhorz){
      # first and second moments
      Mean00  <- Cm %*% Mean00 # Create mean forecast
      Sigma00 <- Cm %*% Sigma00 %*% t(Cm) + Jm %*% S_draw %*% t(Jm) # update variance of forecasts
      
      # draw forecasts from predictive density
      yf    <- Mean00[1:M] + t(chol(Sigma00[1:M, 1:M])) %*% rnorm(M) 
      yf_store[irep-nburn, , ihorz] <- yf
    }

    #---------------------------------------------------------------------------
    # Step 3d: Impulse response functions; both Cholesky and sign restrictions

    #---------------------------------------------------------------------------
    # Step 3e: Identification via Cholesky
    shock.chol <- t(chol(S_draw))
    # Normalise shocks to 1 units
    shock.chol <- diag(1 / diag(shock.chol)) %*% shock.chol
    

    #---------------------------------------------------------------------------
    # Step 3f: Identification via sign-restrictions
    cond.overall <- TRUE
    counter      <- 0
    MaxTries     <- 1000
    # draw rotation matrices Q till you find a fitting one (while-loop)
    while(cond.overall && counter < MaxTries){
      counter <- counter + 1
      
      # Define a rotation matrix with positive values on the main diagonal
      Rtilda <- matrix(rnorm(M^2, 0, 1), M, M)
      qr.object <- qr(Rtilda)
      Q <- qr.Q(qr.object)
      Q <- Q %*% diag((diag(Q) > 0) - (diag(Q) < 0))

      #shock is a full matrix
      shock.chol <- t(chol(S_draw))
      shock.sign <- shock.chol %*% Q

      # Oil supply shock
      cond.OS <- (shock.sign[1, 1] < 0) * (shock.sign[2, 1] < 0) * (shock.sign[3, 1] > 0 )  
      # Oil REA shock 
      cond.REA <- (shock.sign[1, 2] > 0) * (shock.sign[2, 2] > 0) * (shock.sign[3, 2] > 0)  
      # Oil Demand driven shock
      cond.D <- (shock.sign[1, 3] > 0) * (shock.sign[2, 3] < 0) * (shock.sign[3, 3] > 0) 
     
      #assuming other shocks influence price negatively on average
      
      #Shocks have to be mutually exclusive (orthogonal)
      cond.overall <- (cond.OS * cond.REA * cond.D)==0
    }
    cou_store[irep - nburn] <- counter

    #---------------------------------------------------------------------------
    # Step 3g: Compute IRFs
    # Temporary objects for state space representation
    irf.mat.chol<- irf.mat.sign <- array(NA, c(M, M, nhor))

    # Impulse --> shock at t = 0:
    irf.mat.chol[ , , 1] <- shock.chol
    irf.mat.sign[ , , 1] <- shock.sign

    #start at t = 1, as t = 0 is the impulse shock
    Cmi <- Cm
    for(ihorz in 2:nhor){
      irf.mat.chol[ , , ihorz] <- t(Jm) %*% Cmi %*% Jm %*% shock.chol
      irf.mat.sign[ , , ihorz] <- t(Jm) %*% Cmi %*% Jm %*% shock.sign
      Cmi <- Cmi %*% Cm
    }
    IRFchol_store[irep - nburn, , , ] <- irf.mat.chol
    IRFsign_store[irep - nburn, , , ] <- irf.mat.sign
  }
  if(irep %% 50 == 0) print(paste0("Round: ", irep, "/", ntot))
}

# CHECK CONVERGENCE
library(coda)
crit_val <- 1.96
Z_scores <- c()

par(mfrow=c(k,3),mar=c(2,2,1,1))
for(ii in 1:k){
  for(jj in 1:M){
    #plot.ts(A_store[,ii,jj])
    #abline(h = mean(A_store[,ii,jj]), col = "red", lty = 2)
    #abline(h = quantile(A_store[,ii,jj], p = c(0.05, 0.95)), col = "blue")
    Z_scores[(jj-1)*k+ii] <- geweke.diag(A_store[,ii,jj])$z
  }
}


# Autocorrelation of parameter draws for AR coefficients
#par(mfrow=c(k,3),mar=c(1,1,1,1))
#for(ii in 1:k){
#  for(jj in 1:M){
#    acf(A_store[,ii,jj])
#  }
#}



# Autocorrelation of parameter draws for variance coefficients
#par(mfrow=c(M,M),mar=c(1,1,1,1))
#for(jj in 1:M){
#  for(ii in 1:M){
#    acf(S_store[,ii,jj])
#  }
#}

idx <- which(abs(Z_scores) > crit_val)
paste(length(idx), " out of ",k*M+M^2, " variables' z-values exceed the 1.96 threshold", " (", round(length(idx)/(k*M+M^2)*100,2),"%)",sep="")

#Quantiles over the first dimension (number of saved draws)
IRFchol_low    <- apply(IRFchol_store, c(2,3,4), quantile, 0.16,na.rm=TRUE)
IRFchol_high   <- apply(IRFchol_store, c(2,3,4), quantile, 0.84,na.rm=TRUE)
IRFchol_median <- apply(IRFchol_store, c(2,3,4), median, na.rm=TRUE)

IRFsign_low    <- apply(IRFsign_store, c(2,3,4), quantile, 0.16,na.rm=TRUE)
IRFsign_high   <- apply(IRFsign_store, c(2,3,4), quantile, 0.84,na.rm=TRUE)
IRFsign_median <- apply(IRFsign_store, c(2,3,4), median, na.rm=TRUE)





## check signs
par(mfrow=c(1,1))
hist(cou_store)

### plotting predictions
yf_low    <- apply(yf_store, c(2,3), quantile, 0.16, na.rm=TRUE)
yf_median <- apply(yf_store, c(2,3), quantile, 0.50, na.rm=TRUE)
yf_high   <- apply(yf_store, c(2,3), quantile, 0.84, na.rm=TRUE)

yf_low    <- cbind(t(Yraw[(bigT-20):bigT,]),yf_low)
yf_median <- cbind(t(Yraw[(bigT-20):bigT,]),yf_median)
yf_high   <- cbind(t(Yraw[(bigT-20):bigT,]),yf_high)

xax <- c(as.character(time[(bigT-20):bigT]),paste0("t+",seq(1,fhorz)))




```

```{r inactive IRF chol, echo=FALSE, eval=FALSE}
#not used at moment
par(mfrow=c(1,4))
for(ii in 1:M){
  for(jj in 4:4){
    min1 <- min(IRFchol_low[ii,jj,])
    max1 <- max(IRFchol_high[ii,jj,])
   plot.ts(IRFchol_median[ii,jj,], ylab="", main=paste0("Shock ",colnames(Y)[jj], " on ",colnames(Y)[ii]), ylim = c(min1,max1),xaxt="n",lwd=2,xlab="")
    lines(IRFchol_low[ii,jj,], lty = 2, lwd=2)
    lines(IRFchol_high[ii,jj,], lty = 2, lwd=2)
    abline(h=0,col="red",lwd=2)
    abline(v=seq(1,nhor,by=2), col="lightgrey", lty=2)
    axis(1, at=seq(1,nhor,by=2), labels=seq(0,nhor-1,by=2))
  }
}
``` 

```{r inactive IRF SR, echo=FALSE, eval=FALSE}
#not used at moment
par(mfrow=c(3,3),mar=c(4,4,2,2))
for(ii in 1:M){
  for(jj in 1:M){
    min1 <- min(IRFsign_low[ii,jj,])
    max1 <- max(IRFsign_high[ii,jj,])
    plot.ts(IRFsign_median[ii,jj,], ylab="", xlab="", main=paste0("Shock ",colnames(Y)[jj], " on ",colnames(Y)[ii]), ylim = c(min1,max1), xaxt="n",lwd=2)
    lines(IRFsign_low[ii,jj,], lty = 2, lwd=2)
    lines(IRFsign_high[ii,jj,], lty = 2, lwd=2)
    abline(h=0,col="red",lwd=2)
    abline(v=seq(1,nhor,by=2), col="lightgrey", lty=2)
    axis(1, at=seq(1,nhor,by=2), labels=seq(0,nhor-1,by=2))
  }
}
```

## Subquestion 2.2 - Figure 2 Replication 
*Replicate figures 2 and 3 of Kilian, 2009 by recovering the structural form of the model by recursive ordering of variables.*

Below we replicate figure 2.

```{r, echo=FALSE}
# Replicate Fig. 2
err <- t(apply(apply(E_store, c(2, 3), median), 1, function(x) solve(shock.chol) %*% x))
err <- ts(err, start = 1975, frequency = 12)
par(mfrow=c(3,1),mar=c(5,3,2,3))
plot(as.zoo(aggregate.ts(err, FUN = mean))[, 1],
ylim = c(-1, 1), xlab = "", ylab = "", main = "Oil supply shock")
abline(h=0, col="grey")
plot(as.zoo(aggregate.ts(err, FUN = mean))[, 2],
ylim = c(-1, 1), xlab = "", ylab = "", main = "Aggregate demand shock")
abline(h=0, col="grey")
plot(as.zoo(aggregate.ts(err, FUN = mean))[, 3],
ylim = c(-1, 1), xlab = "", ylab = "", main = "Oil-specific demand shock")
abline(h=0, col="grey")

```

\newpage

## Subquestion 2.2 - Figure 3 Replication

Below we replicate figure 3. The IRFs remind of those in the paper by Kilian, but are more smooth with values pushed more towards zero due to our prior. If we wanted to get IRFs which correspond more to those in the paper, we could increase the value of $\lambda_1$.

```{r figure 3, echo=FALSE}
# Code for replication of figure 3:
IRFchol_store_tmp <- IRFchol_store
for (i in 1:3) {
  IRFchol_store_tmp[, 1, i, ] <- t(apply(IRFchol_store[, 1, i, ], 1, cumsum))
}

#Quantiles over the first dimension (number of saved draws)
IRFchol_low    <- apply(IRFchol_store_tmp, c(2,3,4), quantile, 0.16,na.rm=TRUE)
IRFchol_high   <- apply(IRFchol_store_tmp, c(2,3,4), quantile, 0.84,na.rm=TRUE)
IRFchol_median <- apply(IRFchol_store_tmp, c(2,3,4), median, na.rm=TRUE)

#changing signs of the Cholesky decomposition for the oil supply shock
for(jj in 1:3){
  for(ii in 1:16){
    IRFchol_low[jj,1,ii] <- (-1)* IRFchol_low[jj,1,ii]
    IRFchol_high[jj,1,ii] <- (-1)* IRFchol_high[jj,1,ii]
    IRFchol_median[jj,1,ii] <- (-1)* IRFchol_median[jj,1,ii]
}}
  

#Start plotting the IRFs w.r.t. different shocks
yaxis <- list(c(-25, 15), 
               c(-5, 10), 
               c(-5, 10))

par(mfrow=c(3,3),mar=c(2,2,1,1))

for(jj in 1:3){
  for(ii in 1:3){
    plot.ts(IRFchol_median[ii,jj,], ylab="", xlab="", main=paste0("Shock ",colnames(Y)[jj], " on ",colnames(Y)[ii]), xaxt="n",lwd=2,       ylim = yaxis[[ii]])
    lines(IRFchol_low[ii,jj,], lty = 2, lwd=2)
    lines(IRFchol_high[ii,jj,], lty = 2, lwd=2)
    abline(h=0,col="red",lwd=2)
    abline(v=seq(1,nhor,by=2), col="lightgrey", lty=2)
    axis(1, at=seq(1,nhor,by=2), labels=seq(0,nhor-1,by=2))
              }
            }
```


## Subquestion 2.3 - Sign Restrictions
*Think of reasonable sign restrictions to identify the model at hand; discuss and implement them. Recreate figure 3 using these restrictions and discuss differences to the one identified by recursive ordering. Briefly discuss potential shortcomings of both identifcation schemes.*

We propose the following sign restrictions, based on Kilian & Murphy (2012). It might be important to note here that the proposed columns are not linear combinations of each other, which would result in the model not being identified. 

\begin{equation}
\begin{bmatrix}
e^{OP} \\
e^{RA} \\
e^{P} \\
\end{bmatrix}
=
\begin{bmatrix}
- & + & + \\
- & + & - \\
+ & + & + \\
\end{bmatrix}
\begin{bmatrix}
e^{OS} \\
e^{AD} \\
e^{OD} \\
\end{bmatrix}
\end{equation}

The shortcoming of both identifications schemes comes from their definition. A *zero short run restriction* assumes that some variables do not react contemporaneously to a shock of other variables. The sign restrictions assume that reaction of some of the variables to a shock to other variables are positive or negative. Additionally when using sign restrictions the causal coefficients are set identified, which gives rise to larger confidence bands. 

```{r SR}
# Code for replication sign restriction 
#New storage for cumulative IRFs
IRFsign_store_tmp <- IRFsign_store

for (i in 1:3) {
  IRFsign_store_tmp[, 1, i, ] <- t(apply(IRFsign_store[, 1, i, ], 1, cumsum))
}

#Quantiles over the first dimension (number of saved draws)
IRFsign_low    <- apply(IRFsign_store_tmp, c(2,3,4), quantile, 0.16,na.rm=TRUE)
IRFsign_high   <- apply(IRFsign_store_tmp, c(2,3,4), quantile, 0.84,na.rm=TRUE)
IRFsign_median <- apply(IRFsign_store_tmp, c(2,3,4), median, na.rm=TRUE)

#changing signs of the Cholesky decomposition for the oil supply shock
for(jj in 1:3){
  for(ii in 1:16){
    IRFsign_low[jj,1,ii] <- (-1)* IRFsign_low[jj,1,ii]
    IRFsign_high[jj,1,ii] <- (-1)* IRFsign_high[jj,1,ii]
    IRFsign_median[jj,1,ii] <- (-1)* IRFsign_median[jj,1,ii]
}}
  
#Start plotting the IRFs w.r.t. different shocks
yaxis <- list(c(-25, 15), 
               c(-5, 10), 
               c(-5, 10))

par(mfrow=c(3,3),mar=c(2,2,1,1))

for(jj in 1:3){
  for(ii in 1:3){
    plot.ts(IRFsign_median[ii,jj,], ylab="", xlab="", main=paste0("Shock ",colnames(Y)[jj], " on ",colnames(Y)[ii]), xaxt="n",lwd=2,       ylim = yaxis[[ii]])
    lines(IRFsign_low[ii,jj,], lty = 2, lwd=2)
    lines(IRFsign_high[ii,jj,], lty = 2, lwd=2)
    abline(h=0,col="red",lwd=2)
    abline(v=seq(1,nhor,by=2), col="lightgrey", lty=2)
    axis(1, at=seq(1,nhor,by=2), labels=seq(0,nhor-1,by=2))
              }
            }
```


\newpage

## Subquestion 2.4 - Other Variables
*Think of other variables that might be influenced by oil market shocks and collect data that fits the frequency and time period of the provided data. Transform the additional data appropriately and estimate the reduced form of a suitable VAR model. Identify the different shocks (using recursive ordering and sign restrictions), compute impulse responses and discuss your results.*


We decided to use the Variable "S.P.500" from the dataset "current.csv" and as a measure for the CPI the Variable "CPIAUCSL". 

```{r Data SP500}
FRED <- read.csv("current.csv",sep = ",", dec = ".")[-1,]
data.SP.CPI.raw <- ts(FRED[c("S.P.500","CPIAUCSL")], start=c(1959,1),frequency=12)
data.SP.CPI <- window(data.SP.CPI.raw, start = c(1973, 1), end = c(2006, 12))
data.returns.inf <- diff(log(data.SP.CPI)) * 100
SP.RR <- (1 + data.returns.inf[,1]) / (1 + data.returns.inf[,2]) - 1

data.returns <- ts(data.frame(data.kilian[,1:3], SP.RR), start = c(1972, 12), frequency=12)

Traw <- nrow(data.returns)
Yraw <- data.returns
```

We again estimate the VAR...

```{r transform SP500, echo=FALSE, include=FALSE}
#------------------------------------------------------------------------------------
# useful function for lagging data matrices
mlag <- function(X,lag){
  p <- lag
  X <- as.matrix(X)
  Traw <- nrow(X)
  N <- ncol(X)
  Xlag <- matrix(0,Traw,p*N)
  for (ii in 1:p){
    Xlag[(p+1):Traw,(N*(ii-1)+1):(N*ii)]=X[(p+1-ii):(Traw-ii),(1:N)]
  }
  return(Xlag)
}
#######################################################################################
### Independent normal-Wishart prior for the VAR
######################################################################################
# needed libraries
library(MCMCpack) # has the inverse wishart riwish()
library(magic)

# specifications
plag <- 24     # number of lags
cons <- TRUE  # include constant?

# Create data matrices
Yraw <- as.matrix(Yraw)
Xraw <- mlag(Yraw, plag) # X's are the lagged values of Y

if(cons) Xraw <- cbind(Xraw, 1) # Note that constant is located after lags of variables

# look at size of data
dim(Yraw)
dim(Xraw)

# first plag rows are zero | conditioning on the first p observations
Y <- Yraw[(plag + 1):nrow(Yraw), ]
X <- Xraw[(plag + 1):nrow(Xraw), ]
y <- as.vector(Y)

dim(Y)
dim(X)
# View(X)

# get useful dimensions
M    <- ncol(Y)           # number of endogenous variables in the VAR
bigT <- nrow(Y)           # sample size, do not use T only as name!
K    <- M * plag          # number of autoregressive coefficients
k    <- ncol(X)           # number of parameters per equation
v    <- M * (M - 1) / 2
#------------------------------------------------------------------------------------
# Initial Values, OLS preliminaries, can also just take a draw from the prior distribution
#------------------------------------------------------------------------------------
A_OLS <- solve(crossprod(X)) %*% crossprod(X, Y)
# A_OLS <- chol2inv(chol(crossprod(X)))%*%crossprod(X,Y) 
# Cholesky to inverse saves computation time
E_OLS <- Y - X %*% A_OLS
S_OLS <- crossprod(E_OLS) / (bigT - K)

# let's have a look at OLS estimates
yfit <- X %*% A_OLS
# amazing in-sample fit, but bad out-of-sample fit
library(zoo)
time <- as.yearqtr(time(data.returns))



# explained variation
diag(crossprod(yfit)) / diag(crossprod(Y))
```

```{r main SP500, echo=FALSE, include=FALSE}
#------------------------------------------------------------------------------------
# PRIORS
#------------------------------------------------------------------------------------
A_prior <- matrix(0, k, M) 
diag(A_prior) <- 1 # prior mean: 1 for first own lags, 0 otherwise. Note that prior mean for
                   # deterministics is in last row due to ordering of constant in Xraw
A_prior
a_prior <- as.vector(A_prior) # vectorize prior mean matrix

# get AR variances to scale cross-variable lags of Minnesota prior
sigs <- numeric(length = M)
for(mm in 1:M){
  yuse <- Y[, mm, drop=FALSE]
  xuse <- cbind(X[,seq(mm, M * plag, by=M), drop=FALSE], 1)
  b    <- solve(crossprod(xuse)) %*% crossprod(xuse,yuse)
  sigs[mm] <- crossprod(yuse-xuse %*% b) / (bigT - plag - 1)
}

# Minnesota prior
# own lags:       (lambda1/k)^2   # k == lag
# cross lags:     (sig_i^2/sig_j^2)(lambda1 * lambda2/k)^2
# deterministics: lambda3*sig_i^2
lambda1 <- 0.6; lambda2 <- 0.5; lambda3 <- 100
V_prior <- array(0, c(k, k, M))
for(mm in 1:M){ # over all equations
  for(pp in 1:plag){ # over all lags
    for(kk in 1:M){ # over all coefficients
      if(mm == kk){ # own lag
        V_prior[(pp - 1) * M + kk, (pp - 1) * M + kk, mm] <- (lambda1 / pp)^2
      }else{ # cross-lags
        V_prior[(pp - 1) * M + kk, (pp - 1) * M + kk, mm] <- (sigs[mm] / sigs[kk]) * (lambda1 * lambda2 / pp)^2
      }
    }
  }
  V_prior[k, k, mm] <- lambda3 * sigs[mm] # for deterministics (i.e. constant)
}
V_prior    <- lapply(seq(dim(V_prior)[3]), function(x) V_prior[ , , x]) # array to list
V_prior    <- Reduce(magic::adiag, V_prior) # bring in form
V_prior[1:(M*plag+1), 1:(M*plag+1)]
V_priorinv <- diag(1 / diag(V_prior))

# hyperparameters for inverse Wishart
s0 <- M + 2
S0 <- (s0 - M - 1) * diag(sigs)

# initialize draws with OLS estimators
A_draw <- A_OLS
S_draw <- S_OLS

# outside loop calculations
s_post    <- bigT + s0
XX <- crossprod(X)


#------------------------------------------------------------------------------------
# MCMC setup
#------------------------------------------------------------------------------------
nsave <- 100               # number of saved draws
nburn <- 50               # number of burned draws
ntot  <- nsave + nburn      # number of total draws
nhor  <- 16                 # horizon for IRFs
fhorz <- 8                  # forecasting horizon

# Container for MCMC draws, stored after burn-in
A_store <- array(NA, c(nsave, k, M))
S_store <- array(NA, c(nsave, M, M))

# container for sign restriction attempts
cou_store <- numeric(length = nsave)

# Predictions -- dimensions: number of draws x number of variables x forecasting horizon
yf_store <- array(NA, c(nsave, M, fhorz))

# IRFs -- dimensions: Number of draws x Number of responses x Number of structural shocks x horizon
IRFchol_store <- array(NA,c(nsave, M, M, nhor))
IRFsign_store <- array(NA,c(nsave, M, M, nhor))


set.seed(1)
for(irep in 1:ntot){
  #-----------------------------------------------------------------------------
  # Step 1: Draw S_draw | Y, A_draw from IW
  # s_overbar = T + s_underbar (s0)
  # S_overbar = (Y-XA)'(Y-XA) + S_underbar (S0)
  # SIGMA | Y ~ iW(s_overbar,S_overbar)
 
  S_post    <- crossprod(Y - X %*% A_draw)
  S_drawinv <- matrix(rWishart(1,s_post,solve(S_post)),M,M) 
  # note that we can draw from the Wishart and inverting leads to the inverse-Wishart
  S_draw    <- solve(S_drawinv) 
  # or using the MCMCpack to draw from inverse-Wishart directly
  S_draw    <- MCMCpack::riwish(s_post, S_post)

  #-----------------------------------------------------------------------------
  # Step 2: Draw A_draw | Y, S_draw from multivariate normal
  # V_overbar = (SIGMAinv otimes X'X + Vinv_underbar)^{-1}
  # a_overbar = V_overbar (Vinv_underbar a_underbar + (SIGMAinv otimes X')y)
  V_post    <- solve(kronecker(S_drawinv, XX) + V_priorinv)
  # Here, using chol2inv(chol(kronecker(S_drawinv, XX) + V_priorinv)) saves time
  A_post    <- V_post %*% (kronecker(S_drawinv, t(X))%*%y + V_priorinv%*%a_prior)
  
  eig_check <- TRUE
  while(eig_check) {
    # Here, using the lower Cholesky factor multiplied by k * M Normal draws creates
    # draws from the multivariate Normal and saves time, compared to drawing from 
    # multivariate Normal directly
    A_draw     <- matrix(A_post + t(chol(V_post)) %*% rnorm(k * M), k, M)
    # stability check using companion form
    Cm <- matrix(0, K, K)
    Cm[1:M,] <- t(A_draw[1:K, ]) # companion matrix excludes deterministic terms
    diag(Cm[(M + 1):K, 1:(M * (plag - 1))]) <- 1
    
    eig_check <- max(abs(Re(eigen(Cm)$values))) > 1
  }
  
  #-----------------------------------------------------------------------------
  # Step 3: Storage/Predictions/IRFs
  if(irep > nburn){
    # Step 3a: Save parameter draws
    A_store[irep - nburn, , ] <- A_draw
    S_store[irep - nburn, , ] <- S_draw
  
    
    #---------------------------------------------------------------------------
    # Step 3b: Build companion matrix for forecasts and IRFs again (illustration)
    Cm <- matrix(0, K, K)
    Cm[1:M,] <- t(A_draw[1:K, ]) # companion matrix excludes deterministic terms
    diag(Cm[(M + 1):K, 1:(M * (plag - 1))]) <- 1
    Jm <- matrix(0, K, M)
    diag(Jm) <- 1

    #---------------------------------------------------------------------------
    # Step 3c: Do predictions and calculate fhorz-step ahead prediction density
    Mean00  <- c(Y[bigT, ], X[bigT, 1:(M * (plag - 1))]) 
    # take latest values for Y plus p-1 lags from X for forecasts
    Sigma00 <- matrix(0, K, K)
    for(ihorz in 1:fhorz){
      # first and second moments
      Mean00  <- Cm %*% Mean00 # Create mean forecast
      Sigma00 <- Cm %*% Sigma00 %*% t(Cm) + Jm %*% S_draw %*% t(Jm) # update variance of forecasts
      
      # draw forecasts from predictive density
      yf    <- Mean00[1:M] + t(chol(Sigma00[1:M, 1:M])) %*% rnorm(M) 
      yf_store[irep-nburn, , ihorz] <- yf
    }

    #---------------------------------------------------------------------------
    # Step 3d: Impulse response functions; both Cholesky and sign restrictions

    #---------------------------------------------------------------------------
    # Step 3e: Identification via Cholesky
    shock.chol <- t(chol(S_draw))
    # Normalise shocks to 1 units
    shock.chol <- diag(1 / diag(shock.chol)) %*% shock.chol
    

    #---------------------------------------------------------------------------
    # Step 3f: Identification via sign-restrictions
    cond.overall <- TRUE
    counter      <- 0
    MaxTries     <- 1000
    # draw rotation matrices Q till you find a fitting one (while-loop)
    while(cond.overall && counter < MaxTries){
      counter <- counter + 1
      
      # Define a rotation matrix with positive values on the main diagonal
      Rtilda <- matrix(rnorm(M^2, 0, 1), M, M)
      qr.object <- qr(Rtilda)
      Q <- qr.Q(qr.object)
      Q <- Q %*% diag((diag(Q) > 0) - (diag(Q) < 0))

      #shock is a full matrix
      shock.chol <- t(chol(S_draw))
      shock.sign <- shock.chol %*% Q

      # Oil supply shock
      cond.OS <- (shock.sign[1, 1] < 0) * (shock.sign[2, 1] < 0) * (shock.sign[3, 1] > 0 )  * (shock.sign[4, 1] < 0 )
      # Oil REA shock 
      cond.REA <- (shock.sign[1, 2] > 0) * (shock.sign[2, 2] > 0) * (shock.sign[3, 2] > 0)  * (shock.sign[4, 2] > 0 )
      # Oil Demand driven shock
      cond.D <- (shock.sign[1, 3] > 0) * (shock.sign[2, 3] < 0) * (shock.sign[3, 3] > 0)  * (shock.sign[4, 3] < 0 )
      # other RDG shocks
      cond.D <- (shock.sign[1, 4] > 0) * (shock.sign[2, 4] > 0) * (shock.sign[3, 4] < 0)  * (shock.sign[4, 4] > 0 )
      #assuming other shocks influence price negatively on average
      
      #Shocks have to be mutually exclusive (orthogonal)
      cond.overall <- (cond.OS * cond.REA * cond.D)==0
    }
    cou_store[irep - nburn] <- counter

    #---------------------------------------------------------------------------
    # Step 3g: Compute IRFs
    # Temporary objects for state space representation
    irf.mat.chol<- irf.mat.sign <- array(NA, c(M, M, nhor))

    # Impulse --> shock at t = 0:
    irf.mat.chol[ , , 1] <- shock.chol
    irf.mat.sign[ , , 1] <- shock.sign

    #start at t = 1, as t = 0 is the impulse shock
    Cmi <- Cm
    for(ihorz in 2:nhor){
      irf.mat.chol[ , , ihorz] <- t(Jm) %*% Cmi %*% Jm %*% shock.chol
      irf.mat.sign[ , , ihorz] <- t(Jm) %*% Cmi %*% Jm %*% shock.sign
      Cmi <- Cmi %*% Cm
    }
    IRFchol_store[irep - nburn, , , ] <- irf.mat.chol
    IRFsign_store[irep - nburn, , , ] <- irf.mat.sign
  }
  if(irep %% 50 == 0) print(paste0("Round: ", irep, "/", ntot))
}

# CHECK CONVERGENCE
library(coda)
crit_val <- 1.96
Z_scores <- c()

par(mfrow=c(k,3),mar=c(2,2,1,1))
for(ii in 1:k){
  for(jj in 1:M){
    #plot.ts(A_store[,ii,jj])
    #abline(h = mean(A_store[,ii,jj]), col = "red", lty = 2)
    #abline(h = quantile(A_store[,ii,jj], p = c(0.05, 0.95)), col = "blue")
    Z_scores[(jj-1)*k+ii] <- geweke.diag(A_store[,ii,jj])$z
  }
}


# Autocorrelation of parameter draws for AR coefficients
#par(mfrow=c(k,3),mar=c(1,1,1,1))
#for(ii in 1:k){
#  for(jj in 1:M){
#    acf(A_store[,ii,jj])
#  }
#}



# Autocorrelation of parameter draws for variance coefficients
#par(mfrow=c(M,M),mar=c(1,1,1,1))
#for(jj in 1:M){
#  for(ii in 1:M){
#    acf(S_store[,ii,jj])
#  }
#}

idx <- which(abs(Z_scores) > crit_val)
paste(length(idx), " out of ",k*M+M^2, " variables' z-values exceed the 1.96 threshold", " (", round(length(idx)/(k*M+M^2)*100,2),"%)",sep="")

#Quantiles over the first dimension (number of saved draws)
IRFchol_low    <- apply(IRFchol_store, c(2,3,4), quantile, 0.16,na.rm=TRUE)
IRFchol_high   <- apply(IRFchol_store, c(2,3,4), quantile, 0.84,na.rm=TRUE)
IRFchol_median <- apply(IRFchol_store, c(2,3,4), median, na.rm=TRUE)

IRFsign_low    <- apply(IRFsign_store, c(2,3,4), quantile, 0.16,na.rm=TRUE)
IRFsign_high   <- apply(IRFsign_store, c(2,3,4), quantile, 0.84,na.rm=TRUE)
IRFsign_median <- apply(IRFsign_store, c(2,3,4), median, na.rm=TRUE)





## check signs
par(mfrow=c(1,1))
hist(cou_store)

### plotting predictions
yf_low    <- apply(yf_store, c(2,3), quantile, 0.16, na.rm=TRUE)
yf_median <- apply(yf_store, c(2,3), quantile, 0.50, na.rm=TRUE)
yf_high   <- apply(yf_store, c(2,3), quantile, 0.84, na.rm=TRUE)

yf_low    <- cbind(t(Yraw[(bigT-20):bigT,]),yf_low)
yf_median <- cbind(t(Yraw[(bigT-20):bigT,]),yf_median)
yf_high   <- cbind(t(Yraw[(bigT-20):bigT,]),yf_high)

xax <- c(as.character(time[(bigT-20):bigT]),paste0("t+",seq(1,fhorz)))




```

... and compute the impulse response functions:

```{r figure 3 SP500 2, echo=FALSE}
# Code for replication of figure 3:
IRFchol_store_tmp <- IRFchol_store
for (i in 1:4) {
  IRFchol_store_tmp[, 1, i, ] <- t(apply(IRFchol_store[, 1, i, ], 1, cumsum))
}

#Quantiles over the first dimension (number of saved draws)
IRFchol_low    <- apply(IRFchol_store_tmp, c(2,3,4), quantile, 0.16,na.rm=TRUE)
IRFchol_high   <- apply(IRFchol_store_tmp, c(2,3,4), quantile, 0.84,na.rm=TRUE)
IRFchol_median <- apply(IRFchol_store_tmp, c(2,3,4), median, na.rm=TRUE)

#changing signs of the Cholesky decomposition for the oil supply shock
for(jj in 1:4){
  for(ii in 1:16){
    IRFchol_low[jj,1,ii] <- (-1)* IRFchol_low[jj,1,ii]
    IRFchol_high[jj,1,ii] <- (-1)* IRFchol_high[jj,1,ii]
    IRFchol_median[jj,1,ii] <- (-1)* IRFchol_median[jj,1,ii]
}}
  

#Start plotting the IRFs w.r.t. different shocks
yaxis <- list(c(-25, 15), 
               c(-5, 6), 
               c(-5, 6),
                c(-2, 5))

par(mfrow=c(4,2),mar=c(2,3,1,2))

for(jj in 1:4){
  for(ii in 1:4){
    plot.ts(IRFchol_median[ii,jj,], ylab="", xlab="", main=paste0("Shock ",colnames(Y)[jj], " on ",colnames(Y)[ii]), xaxt="n",lwd=2,       ylim = yaxis[[ii]])
    lines(IRFchol_low[ii,jj,], lty = 2, lwd=2)
    lines(IRFchol_high[ii,jj,], lty = 2, lwd=2)
    abline(h=0,col="red",lwd=2)
    abline(v=seq(1,nhor,by=2), col="lightgrey", lty=2)
    axis(1, at=seq(1,nhor,by=2), labels=seq(0,nhor-1,by=2))
              }
            }
```

```{r figure 3 SP500, eval=FALSE}
#New storage for cumulative IRFs
IRFchol_store2 <- IRFchol_store

for (i in 1:4) {
IRFchol_store2[, 4, i, ] <- t(apply(IRFchol_store[, 4, i, ], 1, cumsum))
}
#IRFchol_store2[,,3,1] <- IRFchol_store2[,,3,1]*(-1) 
#Quantiles over the first dimension (number of saved draws)
IRFchol_low.68 <- apply(IRFchol_store2, c(2,3,4), quantile, 0.16,na.rm=TRUE)
IRFchol_high.68 <- apply(IRFchol_store2, c(2,3,4), quantile, 0.84,na.rm=TRUE)
IRFchol_low.95 <- apply(IRFchol_store2, c(2,3,4), quantile, 0.025,na.rm=TRUE)
IRFchol_high.95 <- apply(IRFchol_store2, c(2,3,4), quantile, 0.975,na.rm=TRUE)
IRFchol_median2 <- apply(IRFchol_store2, c(2,3,4), median, na.rm=TRUE)
#Start plotting the IRFs w.r.t. different shocks

par(mfrow=c(4,4),mar=c(2,1,1,2))
sign.list <- c(-1,1,1,1)
for(jj in seq_along(sign.list)){
for(ii in 1:4){
plot.ts(sign.list[jj]*IRFchol_median2[ii,jj,], ylab="", main=paste0("Shock ",colnames(Y)[jj], " on ",colnames(Y)[ii]), ylim = c(-5,5),xaxt="n",lwd=2,xlab="")
lines(sign.list[jj]*IRFchol_low.68[ii,jj,], lty = 2, lwd=2)
lines(sign.list[jj]*IRFchol_high.68[ii,jj,], lty = 2, lwd=2)
lines(sign.list[jj]*IRFchol_low.95[ii,jj,], lty = 3, lwd=2)
lines(sign.list[jj]*IRFchol_high.95[ii,jj,], lty = 3, lwd=2)
abline(h=0,col="red",lwd=2)
axis(1, at = seq(1, nhor, by = 2), labels = seq(0, nhor - 1, by = 2))

}}
```

Computing the Impulse Response Functions as always, we can have a look at what the effects of shocks of our original variables on the the S\&P 500 measure are. The left most panel is the cumulative IRF of a shock in oil production, which seems to have little to non-significant effects on our inflation proxy, as can be seen from the confidence intervals. A similar effect can be seen in the shock related to real economic activity, which however shows signs of a decreasing effect in the later periods (starting at roughly period 8) The most significant effect can be seen in the IRF concerning a shock in the real price of oil, which shows to have a significant and sustainable decrease in the deflated stock returns. Similar to our non-bayesian aproach in assignment 1, the results are in line with the ones in Killian & Park (2009).

Sign restrictions:

```{r SR SP500 2}
# Code for replication sign restriction 
#New storage for cumulative IRFs
IRFsign_store_tmp <- IRFsign_store

for (i in 1:4) {
  IRFsign_store_tmp[, 1, i, ] <- t(apply(IRFsign_store[, 1, i, ], 1, cumsum))
}

#Quantiles over the first dimension (number of saved draws)
IRFsign_low    <- apply(IRFsign_store_tmp, c(2,3,4), quantile, 0.16,na.rm=TRUE)
IRFsign_high   <- apply(IRFsign_store_tmp, c(2,3,4), quantile, 0.84,na.rm=TRUE)
IRFsign_median <- apply(IRFsign_store_tmp, c(2,3,4), median, na.rm=TRUE)

#changing signs of the Cholesky decomposition for the oil supply shock
for(jj in 1:4){
  for(ii in 1:16){
    IRFsign_low[jj,1,ii] <- (-1)* IRFsign_low[jj,1,ii]
    IRFsign_high[jj,1,ii] <- (-1)* IRFsign_high[jj,1,ii]
    IRFsign_median[jj,1,ii] <- (-1)* IRFsign_median[jj,1,ii]
}}
  
#Start plotting the IRFs w.r.t. different shocks
yaxis <- list(c(-25, 15), 
               c(-5, 6), 
               c(-5, 6),
                c(-2, 5))

par(mfrow=c(4,2),mar=c(2,3,1,2))

for(jj in 1:4){
  for(ii in 1:4){
    plot.ts(IRFsign_median[ii,jj,], ylab="", xlab="", main=paste0("Shock ",colnames(Y)[jj], " on ",colnames(Y)[ii]), xaxt="n",lwd=2,       ylim = yaxis[[ii]])
    lines(IRFsign_low[ii,jj,], lty = 2, lwd=2)
    lines(IRFsign_high[ii,jj,], lty = 2, lwd=2)
    abline(h=0,col="red",lwd=2)
    abline(v=seq(1,nhor,by=2), col="lightgrey", lty=2)
    axis(1, at=seq(1,nhor,by=2), labels=seq(0,nhor-1,by=2))
              }
            }
```

```{r SR SP500, eval=FALSE}
# Code for replication sign restriction 
#New storage for cumulative IRFs
IRFsign_store2 <- IRFsign_store

for (i in 1:4) {
IRFsign_store2[, 4, i, ] <- t(apply(IRFsign_store[, 4, i, ], 1, cumsum))
}
#Quantiles over the first dimension (number of saved draws)
IRFsign_low.68 <- apply(IRFsign_store2, c(2,3,4), quantile, 0.16,na.rm=TRUE)
IRFsign_high.68 <- apply(IRFsign_store2, c(2,3,4), quantile, 0.84,na.rm=TRUE)
IRFsign_low.95 <- apply(IRFsign_store2, c(2,3,4), quantile, 0.025,na.rm=TRUE)
IRFsign_high.95 <- apply(IRFsign_store2, c(2,3,4), quantile, 0.975,na.rm=TRUE)
IRFsign_median2 <- apply(IRFsign_store2, c(2,3,4), median, na.rm=TRUE)
#Start plotting the IRFs w.r.t. different shocks

par(mfrow=c(4,4),mar=c(2,1,1,2))
sign.list <- c(-1,1,1,1)
main.list <- c("Oil supply shock", "Aggregate demand shock", "Oil-specific demand shock")
for(jj in seq_along(sign.list)){
for(ii in 1:4){
plot.ts(sign.list[jj]*IRFsign_median2[ii,jj,], ylab="", main=paste0("Shock ",colnames(Y)[jj], " on ",colnames(Y)[ii]), ylim = c(-5,5),xaxt="n",lwd=2,xlab="")
lines(sign.list[jj]*IRFsign_low.68[ii,jj,], lty = 2, lwd=2)
lines(sign.list[jj]*IRFsign_high.68[ii,jj,], lty = 2, lwd=2)
lines(sign.list[jj]*IRFsign_low.95[ii,jj,], lty = 3, lwd=2)
lines(sign.list[jj]*IRFsign_high.95[ii,jj,], lty = 3, lwd=2)
abline(h=0,col="red",lwd=2)
axis(1, at = seq(1, nhor, by = 2), labels = seq(0, nhor - 1, by = 2))

}}
```

Again as before, we can see that the confidence intervalls have increased drastically because of the sign restrictions. 